{ \fontfamily{ptm}\selectfont Catalyst Meta Acceleration Framework: The history and the gist of it }

### 2024-11-15 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

\section{Proofs for Catalyst Meta Acceleration}
    In this section, we prove the inexact proximal inequality and give the Nesterov's estimating sequence void of intractable quantities. 
    The notation follows from 
    \hyperref[sec:lin-2015]{Section \ref*{sec:lin-2015}}. 
    Let's now prove the inexact proximal inequality. 
    Recall inexact evaluation $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ such that $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}; y_{k - 1}) \le \epsilon_k$; $x_k^* = \mathcal J_{\kappa^{-1}}y_{k - 1}$ to be the exact evaluation.

>>>>

\section{Proofs for Catalyst Meta Acceleration}
    In this section, we prove the inexact proximal inequality and give the Nesterov's estimating sequence void of intractable quantities. 
    The notation follows from 
    \hyperref[sec:lin-2015]{Section \ref*{sec:lin-2015}}. 
    Let's now prove the inexact proximal inequality. 
    Recall inexact evaluation $x_k \approx \mathcal J_{\kappa^{-1}}y_{k - 1}$ such that $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}}y_{k - 1}; y_{k - 1}) \le \epsilon_k$; $x_k^* = \mathcal J_{\kappa^{-1}}y_{k - 1}$ to be the exact evaluation.
